---
title: 'Lab 5: Continuous Distributions'
author: "Corey Katz"
date: "due 11/6 at end of discussion"
output: 
  pdf_document:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exponential Distribution
The amount of time (in hours) a person spends waiting in a line at the DMV, X, follows and exponential distribution with rate 0.5. 

Q1: What is the expected wait time of this person?
```{r}
#Code
```

Q2: What is the probability that the person waits between 1.5 and 2.5 hours?
```{r}
#Code
```


\newpage
## Continuous Uniform Distribution
In the next 94 minutes an alarm will go off randomly. 

Q3: What is the probability that the alarm goes off in the first 15 minutes?
```{r}
#Code
```

Q4: what is the probability that the alarm goes off in the last 20 minutes?
```{r}
#Code
```

\newpage
## Normal Distribution:
The weights of female giraffes is believed to follow a normal distribution with a mean of 1815 pounds and standard deviation of 100 pounds. 


Q5: What is the z-score of a randomly selected female giraffe the weighs 1600 pounds?
```{r}
#Code
```


Q6: What is the probability that a randomly selected female giraffe is between 1740 lbs. and 2100 lbs.?
```{r}
#Code
```


Q7: What is the probability that a randomly selected giraffes weights over 1810 lbs.?

```{r}
#Code
```


Q8: What is the third quartile of female giraffe weights?
```{r}
#Code
```


Q9: Fill in the blank: The top 10% heaviest female giraffes weigh more than _________ pounds.
```{r}
#Code
```


